R Notebook

### 2017-06-11 doc/RMD/data-comparison.Rmd
add poppr and remove slice to processing
The data processing document was failing in places because I hadn't
loaded poppr. Additionally, readxl updated with the ability to
finally ignore empty rows! Now, slice is no longer needed and
commented out for posterity.

```{r}
library('tidyverse')
library('readxl')
library('assertr')
```

@@

@@

```{r sydney_data}
syd <- read_excel("../Analysis4 ForManu/A1_Copy of binned-genotypes_SE.xlsx", 
                sheet = "GenAlexBinned", skip = 1) %>%
  select(-1) %>%                # removing first column, which is empty
  gather(locus, allele, -1) %>% # gather all loci into tidy columns
  mutate(locus = trimws(locus)) %>% # remove whitespace in locus names
  mutate(allele = as.integer(allele)) %>% # force alleles to integers
  spread(locus, allele) %>%     # spread data out with individual loci in columns
  separate(iso_st_mcg_org_loc_yr_hst_cult_rep, 
           c("Isolate", "Severity", "MCG", "State", "Source", "Year", "Host"), 
           sep = "_") %>%
  mutate_if(is.character, trimws) %>% # Trim whitespace forom all character columns
  mutate(Severity = as.numeric(Severity)) %>%
  mutate(Source = ifelse(Source == "", "unk", Source)) %>%
  slice(-n()) %>% # remove last row
  arrange(Isolate) %>%
  check_data_cromulence
syd
```

@@

```{r read_excel}
ex <- readxl::read_excel("../Analysis4 ForManu/A1_Copy of binned-genotypes_SE.xlsx", sheet = "GenAlex", skip = 1) %>%
  select(-1) %>%                # removing first column, which is empty
  gather(locus, allele, -1) %>% # gather all loci into tidy columns
  mutate(locus = trimws(locus)) %>% # remove (F) designator
  mutate(allele = as.integer(allele)) %>% # force alleles to integers
  spread(locus, allele) %>%
  slice(-n())
ex <- ex[!names(ex) %in% locNames(dat)]

>>>>

```{r}
library('tidyverse')
library('readxl')
library('assertr')
library('poppr')
```

@@

> 2017-06-11: This has been fixed in readxl version 1.0

@@

```{r sydney_data}
syd <- read_excel("../Analysis4 ForManu/A1_Copy of binned-genotypes_SE.xlsx", 
                sheet = "GenAlexBinned", skip = 1) %>%
  select(-1) %>%                # removing first column, which is empty
  gather(locus, allele, -1) %>% # gather all loci into tidy columns
  mutate(locus = trimws(locus)) %>% # remove whitespace in locus names
  mutate(allele = as.integer(allele)) %>% # force alleles to integers
  spread(locus, allele) %>%     # spread data out with individual loci in columns
  separate(iso_st_mcg_org_loc_yr_hst_cult_rep, 
           c("Isolate", "Severity", "MCG", "State", "Source", "Year", "Host"), 
           sep = "_") %>%
  mutate_if(is.character, trimws) %>% # Trim whitespace forom all character columns
  mutate(Severity = as.numeric(Severity)) %>%
  mutate(Source = ifelse(Source == "", "unk", Source)) %>%
  # slice(-n()) %>% # remove last row
  arrange(Isolate) %>%
  check_data_cromulence
syd
```

@@

```{r read_excel}
ex <- readxl::read_excel("../Analysis4 ForManu/A1_Copy of binned-genotypes_SE.xlsx", sheet = "GenAlex", skip = 1) %>%
  select(-1) %>%                # removing first column, which is empty
  gather(locus, allele, -1) %>% # gather all loci into tidy columns
  mutate(locus = trimws(locus)) %>% # remove (F) designator
  mutate(allele = as.integer(allele)) %>% # force alleles to integers
  spread(locus, allele) %>%
  # slice(-n()) %>%
  I()
ex <- ex[!names(ex) %in% locNames(dat)]
